UGAN: Underwater Image Restoration using Generative Adversarial Networks

### 2017-09-12 files/paper/paper.tex
update

\subsection{Network Architecture and Training Details}
Our generator network is a fully convolutional encoder-decoder, similar to the work of \cite{isola2016image}, which is
designed as a ``U-Net'' \cite{ronneberger2015u} due to the structural similarity between input and output.
Encoder-decoder networks downsample (encode) the input via convolutions to a lower dimensional embedding, in which
this embedding is then upsampled (decode) via transpose convolutions to reconstruct the image. The advantage of using
a ``U-Net'' comes from explicitly preserving spatial dependencies produced by the encoder, as opposed to relying on the
embedding to contain all of the information. This is done by the addition of ``skip connections'', which concatenate
the activations produced from a convolution layer $i$ in the encoder to the input of a transpose convolution layer
$n-i+1$ in the decoder, where $n$ is the total number of layers in the network. Each convolutional layer in our
generator uses kernel size $4 \times 4$ with stride 2. Convolutions in the encoder portion of the network are followed
by a leaky ReLU activation with slope $0.02$, while transpose convolutions in the encoder are followed by a ReLU
activation \cite{nair2010rectified}. Excempt from this is the last layer of the decoder, which uses a TanH nonlinearity
to match the input distribution of $[-1, 1]$. Following \cite{radford2015unsupervised}, we use batch normalization
\cite{pmlr-v37-ioffe15} throughout the generator, except for the last layer of the decoder.

Our discriminator is modeled after that of \cite{radford2015unsupervised}, except no batch normalization is used. This
is due to the fact that we penalize the norm of the discriminator's gradient with respect to each input individually,
which batch normalization would invalidate. The authors of \cite{gulrajani2017improved} recommend layer normalization
\cite{ba2016layer}, but we found no significant improvements. In all of our experiments, we use $\lambda_{L1} = 100$,
batch size of 32, Adam Optimizer \cite{kingma2014adam} with learning rate $1e-4$, and train for 100 epochs.
Following WGAN-GP, the discriminator is updated $n$ times for every update of the generator, where $n = 5$. Our
implementation was done using the Tensorflow library \cite{abadi2016tensorflow}.
\footnote{Code is available at https://github.com/cameronfabbri/Underwater-Color-Correction}

@@

\subsection{Evaluation}
We trained UGAN and UGAN-P on the image pairs generated by CycleGAN, and evaluated on the images from the test set, $Y$.
Note that these images do not contain any ground truth, as they are original distorted images from Imagenet. Images for
training and testing are of size $256 \times 256 \times 3$ and normalized between $[-1, 1]$.

>>>>

\subsection{Network Architecture and Training Details}
Our generator network is a fully convolutional encoder-decoder, similar to the work of \cite{isola2016image}, which is
designed as a ``U-Net'' \cite{ronneberger2015u} due to the structural similarity between input and output.
Encoder-decoder networks downsample (encode) the input via convolutions to a lower dimensional embedding, in which
this embedding is then upsampled (decode) via transpose convolutions to reconstruct an image. The advantage of using
a ``U-Net'' comes from explicitly preserving spatial dependencies produced by the encoder, as opposed to relying on the
embedding to contain all of the information. This is done by the addition of ``skip connections'', which concatenate
the activations produced from a convolution layer $i$ in the encoder to the input of a transpose convolution layer
$n-i+1$ in the decoder, where $n$ is the total number of layers in the network. Each convolutional layer in our
generator uses kernel size $4 \times 4$ with stride 2. Convolutions in the encoder portion of the network are followed
by batch normalization \cite{pmlr-v37-ioffe15} and a leaky ReLU activation with slope $0.02$, while transpose
convolutions in the decoder are followed by a ReLU activation \cite{nair2010rectified} (no batch norm in the decoder).
Exempt from this is the last
layer of the decoder, which uses a TanH nonlinearity to match the input distribution of $[-1, 1]$. 
%Batch normalization \cite{pmlr-v37-ioffe15} is used in the encoder portion
%of the generator, but not in the decoder.
%Following \cite{radford2015unsupervised}, we use batch normalization
%\cite{pmlr-v37-ioffe15} throughout the generator, except for the last layer of the decoder.

Our discriminator is modeled after that of \cite{radford2015unsupervised}, except no batch normalization is used. This
is due to the fact that we penalize the norm of the discriminator's gradient with respect to each input individually,
which batch normalization would invalidate. The authors of \cite{gulrajani2017improved} recommend layer normalization
\cite{ba2016layer}, but we found no significant improvements. In all of our experiments, we use $\lambda_{L1} = 100$,
$\lambda_{GP} = 10$, batch size of 32, Adam Optimizer \cite{kingma2014adam} with learning rate $1e-4$, and train for 100 epochs.
Following WGAN-GP, the discriminator is updated $n$ times for every update of the generator, where $n = 5$.
For UGAN-P, we set $\lambda_{IG} = 1.0$.
Our implementation was done using the Tensorflow library \cite{abadi2016tensorflow}.
\footnote{Code is available at https://github.com/cameronfabbri/Underwater-Color-Correction}

@@

\subsection{Evaluation}
We trained UGAN and UGAN-P on the image pairs generated by CycleGAN, and evaluated entirely on the images from the
test set, $Y$. Note that these images do not contain any ground truth, as they are original distorted images from
Imagenet. Images for training and testing are of size $256 \times 256 \times 3$ and normalized between $[-1, 1]$.

%\footnote{Code for inception score can be found at https://github.com/openai/improved-gan}
%\begin{center}
%\begin{tabular}{c c c c c c}
%Samples & real & ugan & ugan-p & cyclegan \\ \hline
%Model & True Images & UGAN & UGAN-P & CycleGAN \\ \hline
%Score $\pm$ std. & $5.69 \pm 0.23$ & $6.18 \pm 0.35$ & $6.30 \pm 0.32$ & $6.37 \pm 0.43$ \\ \hline
%\end{tabular}
%\end{center}
